Effect of character correlation

### 2018-03-22 Analysis/EffectCorrelationFigure.Rmd
added resolution plots

>>>>

## Resolution

How well resolved are the trees?
These graphs represent the number of nodes (i.e. the tree resolution) in the consensus trees for 25, 75 or 50 taxa and 100, 350 or 1000 characters (c).
The solid and dashed lines are respectively the 50% and 95% confidence intervals.
The black dot is the median.

```{r, fig.width=12, fig.height=6}
## Nodes for the trees with 25 taxa
plot.tree.resolution("../Data/Trees_out/Consensus_trees/", ntaxa = 25, col = c("darkgrey", "red", "green3", "blue", "grey", "orange", "lightgreen", "lightblue"))
```

```{r, fig.width=12, fig.height=6}
## Nodes for the trees with 75 taxa
plot.tree.resolution("../Data/Trees_out/Consensus_trees/", ntaxa = 75, col = c("darkgrey", "red", "green3", "blue", "grey", "orange", "lightgreen", "lightblue"))
```

```{r, fig.width=12, fig.height=6}
## Nodes for the trees with 150 taxa
plot.tree.resolution("../Data/Trees_out/Consensus_trees/", ntaxa = 150, col = c("darkgrey", "red", "green3", "blue", "grey", "orange", "lightgreen", "lightblue"))
```
